The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-02 albatros_paper.tex
HCC added a few more red edit notes
HCC started updating schematic for autonomous station

@@

\subsection{Back End Electronics}
\textcolor{red}{\bf Nivek, HCC?} \\
The back end electronics consists of the bias tee, high pass filter
(HPF), low pass filter (LPF) and the Smart Network ADC Processor
(SNAP) board.  The signals are band limited to \SI{1.2}{MHz}-\SI{81}{MHz}.

@@

\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The
SNAP board samples the signals it receives by 250 Msampl/s using
internal ADCs where the signal of the clock is from the Valon 5007
frerquency synthesizer module. This creates a frequency range between
\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
interacts with a raspberry pi and that is where the data is saved.

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
    \caption{Single autonomous station pathfinder}
    \label{Fig:autonomous}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/Signal-Chain.png}
    \caption{Schematic for single autonomous station pathfinder.
      \textcolor{red}{\bf Update this figure and make it similar to
        the two-element schematic.  Tankiso, Nivek, HCC?}}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}

>>>>

\textcolor{red}{\bf Open task for any/all: fix references, make a proper bibtex file}

@@

\subsection{Back-end electronics}
\textcolor{red}{\bf Nivek, HCC?} \\
The back end electronics consists of the bias tee, high pass filter
(HPF), low pass filter (LPF) and the Smart Network ADC Processor
(SNAP) board.  The signals are band limited to \SI{1.2}{MHz}-\SI{81}{MHz}.

@@

\textbf{SNAP Board} - The SNAP board used is specified by Xilinx
Inc. \footnote{http://www.xilinx.com/products/silicon-devices/fpga/kintex-7.html}. The
SNAP board samples the signals it receives by 250 Msampl/s using
internal ADCs where the signal of the clock is from the Valon 5007
frerquency synthesizer module. This creates a frequency range between
\SI{0}{MHz} - \SI{125}{MHz} which contains 2048 channels. A SNAP board
interacts with a raspberry pi and that is where the data is saved.
\textcolor{red}{\bf include text about firmware}

@@

\subsection{Software and data acquisition}
\textcolor{red}{\bf Nivek?} \\
Text goes here.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
    \caption{Single autonomous station pathfinder.  \textcolor{red}{\bf Add command module and electronics glamor shots.}}
    \label{Fig:autonomous}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Schematic for single autonomous station pathfinder.
      \textcolor{red}{\bf Finish updating this figure.  Tankiso, Nivek, HCC?}}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}
